A Comparative Quality Metric for Untargeted Fuzzing with Logic State Coverage

### 2024-09-15 paper/main.tex
Add evaluation plan

  In this work, we propose \emph{logic state coverage} as a proxy metric to
  count observed interesting behaviors. A logic state is a set of satisfied
  branches during one execution, where logic state coverage is the count of
  \emph{individual} observed logic states during a fuzzing campaign. A logic
  state distinguishes less repetitive (i.e., more interesting) behaviors in a
  finer granularity, making the amount of logic state coverage reliably 
  proportional to the number of observed interesting behaviors.
  % 
  We implemented logic state coverage using a bloom filter and reevaluated
  \textsc{FuzzBench} and indecisive-to-subjective fuzzer comparisons in
  hypervisor and grammar fuzzing. 
  % TODO: (The result summary will come here)

@@

\section{Experiment}

@@

\autoref{f:aflpp-xmllint-epfl} shows the preliminary evaluation result
using XMLLint and AFL++. The evaluation was done on a Intel Core i7-8665U CPU
machine with 16 GB of memory. The logic state coverage (left) shows the covered
distinctive logic states over time. The new coverage per second (middle) shows
the number of newly discovered logic states per time, while the new coverage per
execution (right) shows the percentage of executions that discovered new logic
states per execution. \textsc{Avg} indicates the average new coverage per second
or per execution, and \textsc{Ins} indicates the instantaneous new coverage
during the last 10-second measurement frame.

The logic state coverage increases steadily over time, but it gradually slows
down toward the 24-hour mark. This trend is also reflected in the new coverage
plot, where the average new coverage slowly decreases to a steady point toward
the end of the fuzzing campaign.

The sporadic peaks in the instantaneous new coverage plot (\textsc{Ins}) are
mainly due to the favorable in-flight seeds at the moment, which allowed AFL++
to execute XMLLint quicker. This results in more peaks in the "per second" plot
than in the "per execution" plot, where the discovered new logic states were
bigger than the average but the percentage of new logic states per execution
remained low.

%\subsection{Experiment Plan}
%
%\subsection{Measurement Overheads}
%\subsection{General-purpose Fuzzing}
%\subsection{Hypervisor Fuzzing}
  % same cov: what can we learn more from logic state cov?
%\subsection{Grammar Fuzzing}
  % init corpus cov: what can we learn more from logic state cov?

>>>>

  In this work, we propose \emph{logic state coverage} as a proxy metric to
  count observed interesting behaviors. A logic state is a set of satisfied
  branches during one execution, where its coverage is the count of
  \emph{individual} observed logic states during a fuzzing campaign. A logic
  state distinguishes less repetitive (i.e., more interesting) behaviors in a
  finer granularity, making the amount of logic state coverage reliably 
  proportional to the number of observed interesting behaviors.
  % 
  We implemented logic state coverage using a bloom filter and performed a
  preliminary evaluation with AFL++ and XMLLint.
  % reevaluated \textsc{FuzzBench} and indecisive-to-subjective fuzzer
  % comparisons in hypervisor and grammar fuzzing. 
  % TODO: (The result summary will come here)

@@

\section{Evaluation}

@@

\autoref{f:aflpp-xmllint-epfl} shows the preliminary evaluation result
using XMLLint and AFL++. The evaluation was done on an Intel Core i7-8665U CPU
machine with 16 GB of memory. The logic state coverage (left) shows the
distinctive logic states covered over time. The new coverage per second (middle)
shows the number of newly discovered logic states per time, while the new
coverage per execution (right) shows the percentage of executions that
discovered new logic states per execution. \textsc{Avg} indicates the average
new coverage per second or per execution, and \textsc{Ins} indicates the
instantaneous new coverage during the last 10-second measurement frame.

The logic state coverage increases steadily over time but gradually slows
down toward the 24-hour mark. This trend is also reflected in the new coverage
plot, where the average new coverage slowly decreases to a steady point toward
the end of the fuzzing campaign.
%
Notice that the sporadic spikes in the instantaneous new coverage (\textsc{Ins})
are more in the per-second plot than in the per-execution plot, suggesting that
these sudden new coverage surges were primarily caused by quicker execution.

\subsection{Research Questions}

Some of the prime research questions that further evaluation should answer
include the following.

\begin{itemize}
  \item \textbf{RQ1} Can logic state coverage be implemented with all
    requirements in \autoref{s:measure:req} satisfied?
  \item \textbf{RQ2} How does logic state coverage measure the comparative
    quality of popular untargeted fuzzers?
  \item \textbf{RQ3} Can logic state coverage distinguish the quality of the
    fuzzers indistinguishable from conventional edge coverage?
\end{itemize}

For \textbf{RQ1}, the evaluation may evaluate the computation and memory
overhead added by the logic state coverage measurement. It should not perturb
the execution speed of measured fuzzers to minimize the measurement bias. For
\textbf{RQ2}, the evaluation may compare the logic state coverage of popular
untargeted fuzzers \cite{afl,fioraldi2020aflpp,libfuzzer,honggfuzz} with a
set of standard fuzzing targets (e.g., FuzzBench \cite{metzman2021fuzzbench}).
For \textbf{RQ3}, the evaluation may compare the logic state coverage of
specialized fuzzers (e.g., hypervisor fuzzers
\cite{liu2023videzzo,myung2022mundofuzz,sergej2021nyx,schumilo2020hypercube} and
grammar fuzzers
\cite{wang2023fuzzjit,wu2023jitfuzz,gross2023fuzzilli,srivastava2021gramatron,chen2021polyglot}),
whose quality has not been well-distinguished by a conventional edge coverage
metric.

%\subsection{Measurement Overheads}
%\subsection{General-purpose Fuzzing}
%\subsection{Hypervisor Fuzzing}
  % same cov: what can we learn more from logic state cov?
%\subsection{Grammar Fuzzing}
  % init corpus cov: what can we learn more from logic state cov?
